### 2015-05-15 whoop.tex
reworded a footnote

Our approach considers, for a given driver, every pair of entry points that can potentially execute concurrently.  For each such pair, we use symbolic verification to check whether it is possible for the pair to race on a shared memory location. We soundly model the effects of additional entry points by treating the driver shared state abstractly: when an entry point reads from the shared state, a nondeterministic value is returned.  Restricting to pairs of entry points, rather than analyzing all entry points simultaneously, exploits the fact that data races occur between pairs of threads and limits the complexity of the generated verification conditions.\footnote{In principle, our approach could be applied at a coarser level of granularity: e.g.\ by considering all entry points one after the other, taking into account that an entry point can race with itself. However, using pairwise analysis has the additional advantage that it enables us to easily run the analysis for each pair in parallel for performance, although we leave this for future work.}  The trade-off is that a quadratic number of entry point pairs must be checked.  In \S\ref{sec:implementation} we discuss optimizations based on device driver domain knowledge to reduce the number of pairs to some extent.

>>>>

Our approach considers, for a given driver, every pair of entry points that can potentially execute concurrently.  For each such pair, we use symbolic verification to check whether it is possible for the pair to race on a shared memory location. We soundly model the effects of additional entry points by treating the driver shared state abstractly: when an entry point reads from the shared state, a nondeterministic value is returned.  Restricting to pairs of entry points, rather than analyzing all entry points simultaneously, exploits the fact that data races occur between pairs of threads and limits the complexity of the generated verification conditions.\footnote{In principle, our approach could be applied at a coarser level of granularity: e.g.\ by considering all entry points one after the other, taking into account that an entry point can race with itself. However, using pairwise analysis has the additional advantage that it enables us to easily run the analysis for each pair in parallel (for performance), although we leave this for future work.}  The trade-off is that a quadratic number of entry point pairs must be checked.  In \S\ref{sec:implementation} we discuss optimizations based on device driver domain knowledge to reduce the number of pairs to some extent.
